Continuous developmental change can explain discontinuities in word learning

### 2019-01-31 cogsci/cogsci.Rmd
second version cogsci

An unexpected outcome was that adult participants deviated slightly from the model's predicted numbers. While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is different (and vice-versa), adult participants showed the opposite pattern. This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are highly sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa). \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}

>>>>

An unexpected outcome was that adult participants deviated slightly from the model's predicted numbers. While the model predicted recognition accuracy to be more sensitive to object distance when sound distance is high (and vice-versa), adult participants showed the opposite pattern. This deviation is interesting as it suggests that participants adapt their auditory-visual cue integration strategy to the ambiguity of the situation: They are more sensitive to the presence or absence of disambiguating visual information when sound ambiguity is higher (and vice-versa). \footnote{It is unclear whether the same pattern is found in children as the difference between accuracy scores is generally small compared to the uncertainty of the measurements.}
